---
title: "Schema boards: Analyzing everything"
output:
  html_document:
    number_sections: false
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

# Setup: load data, define variables, etc

```{r load-data-define-variables}

rm(list=ls())

source('./scripts/utils/load_all_libraries.R')

qc_filter <- T

source('./scripts/utils/load_transform_data.R')

qc_table <- import('./results/qc_check_sheets/qc_table.csv')

if (qc_filter){
        
        qc_pass_ptp <- qc_table %>%
                filter(!qc_fail_overall) %>%
                select(ptp) %>% .[[1]]
        
        
        data_summary <- data_summary %>%
                filter(ptp %in% qc_pass_ptp)
        long_data <- long_data %>%
                filter(ptp %in% qc_pass_ptp)        
        
}

## BF test against 0 
reportBF = function(x, digits){
        round(as.numeric(as.vector(x)), digits)
}

```

# Normality checks

## Block 2

```{r block-2-normality-checks}

data_summary %>%
        # filter(type == 'all_pa') %>%
        droplevels() %>%
        ggqqplot(x = 'block_2_mouse_error_mean') +
        ggtitle('All PA: QQ Plots') +
        facet_wrap(~type)

# Draw a histogram
data_summary %>%
        # filter(type == 'all_pa') %>%
        droplevels() %>%
        ggplot(aes(x=block_2_mouse_error_mean)) +
        geom_histogram() +
        facet_wrap(~type)


data_summary %>%
        mutate(block_2_mouse_error_mean_LOG = log(block_2_mouse_error_mean)) %>%
        # filter(type == 'all_pa') %>%
        droplevels() %>%
        ggqqplot(x = 'block_2_mouse_error_mean_LOG') +
        ggtitle('All PA: QQ Plots LOG transformed')+
        facet_wrap(~type)

# Draw a histogram
data_summary %>%
        mutate(block_2_mouse_error_mean_LOG = log(block_2_mouse_error_mean)) %>%        
        filter(type == 'all_pa') %>%
        droplevels() %>%
        ggplot(aes(x=block_2_mouse_error_mean_LOG)) +
        geom_histogram()+
        facet_wrap(~type)

```


# Plot mouse clicks

```{r mouse-heat-plots, fig.width=15, fig.height=20}

long_data %>%
        filter(block == 2) %>%
        droplevels() %>%
        ggplot(aes(mouse_clientX - left_offset,mouse_clientY - top_offset)) +
        geom_point(alpha=0.3) +
        geom_point(aes(pa_center_x - left_offset,pa_center_y - top_offset),
                   color='red',
                   size=2) +
        # geom_density_2d_filled(alpha = 0.3) +
        facet_grid(ptp~condition) +
        ggtitle('block 2: Mouse click locations relative to PA')

```

# Learning curve plots

## All data, each condition

```{r raw-learning-curves-and-fits, fig.width=13, fig.height=20}


# Plot the fits
fig_each_ptp <- mean_by_rep_long_all_types %>%
        filter(hidden_pa_img_type == 'all',
               border_dist_closest == 'all') %>%
        droplevels() %>%        
        ggplot(aes(x=hidden_pa_img_row_number_across_blocks,
                   y=mouse_error_mean)) +
        geom_vline(xintercept = 4.5, linetype = 'dashed') +
        
        geom_point(alpha=0.5) +
        geom_line(alpha=0.5) +        
        
        facet_grid(ptp~condition) +
        ggtitle(paste('Mouse euclidean distance',sep='')) +
        xlab('Image repetition') +
        ylab('Mouse euclidean distance ') +
        scale_x_continuous(breaks=c(1,2,3,4,5,6,7,8)) +
        scale_y_continuous(breaks=seq(0,250,50)) +
        theme(legend.position = '') +
        theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank())

print(fig_each_ptp)

```

## All data, overlaid

```{r learning-curves-across-part, fig.width=5, fig.height=4}

# Plot the fits
fig_each_ptp <- mean_by_rep_long_all_types %>%
        filter(hidden_pa_img_type == 'all',
               border_dist_closest == 'all') %>%
        droplevels() %>%                
        group_by(condition,
                 hidden_pa_img_row_number_across_blocks) %>%
        summarise(n = n(),
                  mouse_error_mean_across_ptp = mean(mouse_error_mean,na.rm = T)) %>% 
        ungroup() %>%
        ggplot(aes(x=hidden_pa_img_row_number_across_blocks,
                   y=mouse_error_mean_across_ptp,
                   color=condition)) +
        geom_point() +
        geom_line() +

        # facet_grid(~condition) +
        ggtitle(paste('Mouse euclidean distance; Across participants',sep='')) +
        xlab('Image repetition') +
        ylab('Mouse euclidean distance ') +
        scale_x_continuous(breaks=c(1,2,3,4,5,6,7,8)) +
        # theme(legend.position = 'top') +
        geom_vline(xintercept = 4.5, linetype = 'dashed') 


print(fig_each_ptp)


```

## Near vs far

```{r landmark-raw-learning-curves-and-fits, fig.width=10, fig.height=12}

# For mouse euclidean distance

fig_each_ptp_lm <- mean_by_rep_long_all_types %>%
        filter(hidden_pa_img_type %in% c('near','far'),
               !condition %in% c('random_locations','no_schema'),
               border_dist_closest == 'all'
               ) %>%
        droplevels() %>%
        
        ggplot(aes(x=hidden_pa_img_row_number_across_blocks,
                   y=mouse_error_mean,
                   group=hidden_pa_img_type,
                   color=hidden_pa_img_type)) +
        geom_point(size=1) +
        geom_line(size=0.5) +

        facet_grid(ptp~condition) +
        ggtitle('Mouse euclidean distance') +
        xlab('Image repetition') +
        ylab('Mouse euclidean distance') +
        scale_x_continuous(breaks=c(1,2,3,4,5,6,7,8)) +
        scale_y_continuous(breaks=seq(0,250,50)) +

        # theme(legend.position = 'top') +
        geom_vline(xintercept = 4.5, linetype = 'dashed') +
        # theme(legend.position = '') +
        theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank())        


print(fig_each_ptp_lm)


```

## Near vs far, across-participants

```{r landmark-raw-learning-curves-and-fits-overlaid, fig.width=8, fig.height=5}

# For mouse euclidean distance

fig_each_ptp_lm <- mean_by_rep_long_all_types %>%
        filter(hidden_pa_img_type %in% c('near','far'),
               !condition %in% c('random_locations','no_schema'),
               border_dist_closest == 'all'
               ) %>%
        droplevels() %>%
        
        group_by(condition,
                 hidden_pa_img_type,
                 hidden_pa_img_row_number_across_blocks) %>%
        summarise(n = n(),
                  mouse_error_mean_across_ptp = mean(mouse_error_mean,na.rm = T)) %>% 
        ungroup() %>%
        ggplot(aes(x=hidden_pa_img_row_number_across_blocks,
                   y=mouse_error_mean_across_ptp,
                   color=condition,
                   linetype=hidden_pa_img_type)) +        
        
        geom_point(size=1) +
        geom_line(size=0.5) +

        ggtitle('Mouse euclidean distance') +
        xlab('Image repetition') +
        ylab('Mouse euclidean distance') +
        scale_x_continuous(breaks=c(1,2,3,4,5,6,7,8)) +
        scale_y_continuous(breaks=seq(0,250,50)) +

        # theme(legend.position = 'top') +
        geom_vline(xintercept = 4.5, linetype = 'dashed') +
        # theme(legend.position = '') +
        theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank())        


print(fig_each_ptp_lm)


```


## Near vs far difference across trials:

```{r near-far-diff-across-reps, fig.width=10, fig.height=7}

fig <- mean_by_rep_long_all_types %>%
        filter(hidden_pa_img_type %in% c('near','far'),
               !condition %in% c('random_locations','no_schema'),
               border_dist_closest == 'all'
               ) %>%
        droplevels() %>%

        pivot_wider(id_cols = c(ptp,
                                counterbalancing,
                                condition,
                                hidden_pa_img_row_number_across_blocks),
                    names_from = hidden_pa_img_type,
                    values_from = mouse_error_mean) %>% 
        mutate(far_minus_near = far - near) %>% 
        
        
        ggplot(aes(x=hidden_pa_img_row_number_across_blocks,
                   y=far_minus_near,
                   color=condition,
                   group=condition)) +        
        
        geom_point(size=1) +
        geom_line(size=0.5) +

        facet_wrap(~ptp) +
        ggtitle('Mouse euclidean distance') +
        xlab('Image repetition') +
        ylab('Mouse euclidean distance') +
        scale_x_continuous(breaks=c(1,2,3,4,5,6,7,8)) +
        scale_y_continuous(breaks=seq(0,250,50)) +

        # theme(legend.position = 'top') +
        geom_vline(xintercept = 4.5, linetype = 'dashed') +
        geom_hline(yintercept = 0, linetype = 'dashed') +
        # theme(legend.position = '') +
        theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank())        


print(fig)


```

## Near vs far diff, across participants:

```{r near-far-diff-across-reps-overlaid, fig.width=7, fig.height=5}

fig <- mean_by_rep_long_all_types %>%
        filter(hidden_pa_img_type %in% c('near','far'),
               !condition %in% c('random_locations','no_schema'),
               border_dist_closest == 'all'
               ) %>%
        droplevels() %>%

        pivot_wider(id_cols = c(ptp,
                                counterbalancing,
                                condition,
                                hidden_pa_img_row_number_across_blocks),
                    names_from = hidden_pa_img_type,
                    values_from = mouse_error_mean) %>% 
        mutate(far_minus_near = far - near) %>% 
        
        group_by(condition,
                 hidden_pa_img_row_number_across_blocks) %>%
        summarise(n = n(),
                  far_minus_near_mean_across_ptp = mean(far_minus_near,na.rm = T)) %>% 
        ungroup() %>%

        ggplot(aes(x=hidden_pa_img_row_number_across_blocks,
                   y=far_minus_near_mean_across_ptp,
                   color=condition,
                   group=condition)) +        
        
        geom_point(size=1) +
        geom_line(size=0.5) +

        ggtitle('Mouse euclidean distance') +
        xlab('Image repetition') +
        ylab('Mouse euclidean distance') +
        scale_x_continuous(breaks=c(1,2,3,4,5,6,7,8)) +
        scale_y_continuous(breaks=seq(0,250,50)) +

        # theme(legend.position = 'top') +
        geom_vline(xintercept = 4.5, linetype = 'dashed') +
        geom_hline(yintercept = 0, linetype = 'dashed') +
        # theme(legend.position = '') +
        theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank())        


print(fig)


```

# Block 2 mean performance:

## Compare conditions, across PAs:

```{r block-2-conditions}

data_summary %>%
        filter(type == 'all_pa') %>%
        droplevels() %>%
        
        ggplot(aes(x=condition,
                   y=block_2_mouse_error_mean)) +
        geom_violin() +
        geom_boxplot(width=0.1,
                     fatten=4,
                     outlier.shape = '') +
        geom_jitter(height = 0,
                    width = 0.06,
                    alpha = 0.3) +
        stat_summary(fun=mean,
                     color='red',
                     size=1) +
        ggtitle('Block 2, comparing conditions')

```



## Near vs Far within each condition:

```{r block-2-conditions-near-far}

data_summary %>%
        filter(type != 'all_pa') %>%
        droplevels() %>%
        
        pivot_wider(id_cols = c(ptp,
                                counterbalancing,
                                condition),
                    names_from = type,
                    values_from = block_2_mouse_error_mean) %>% 
        mutate(far_minus_near = far - near) %>%
        
        ggplot(aes(x=condition,
                   y=far_minus_near)) +
        geom_violin() +
        geom_boxplot(width=0.1,
                     fatten=4,
                     outlier.shape = '') +
        geom_jitter(height = 0,
                    width = 0.06,
                    alpha = 0.3) +
        stat_summary(fun=mean,
                     color='red',
                     size=1) +
        ggtitle('Block 2, comparing conditions, Far-Near') +
        geom_hline(yintercept = 0, linetype = 'dashed')

```

### Bayes Factor

```{r bayes-analysis-schema-c-far-vs-near}

data_for_bf_1 <- data_summary %>%
        filter(type != 'all_pa') %>%
        droplevels() %>%
        
        pivot_wider(id_cols = c(ptp,
                                counterbalancing,
                                condition),
                    names_from = type,
                    values_from = block_2_mouse_error_mean) %>% 
        mutate(far_minus_near = far - near) %>%
        select(far_minus_near) %>% .[[1]]


null_interval <- c(0,Inf)

bf <- reportBF(ttestBF(
        data_for_bf_1,
        nullInterval = null_interval
)[1],4)

```


# Near PAs: schema-C vs schema-l

## Plot:

```{r near-pa-schema-c-vs-schema-l, fig.width=3, fig.height=4}

data_summary %>%
        filter(type == 'near') %>%
        droplevels() %>%
        
        pivot_wider(id_cols = c(ptp,
                                counterbalancing,
                                type),
                    names_from = condition,
                    values_from = block_2_mouse_error_mean) %>% 
        mutate(schema_c_minus_schema_l = schema_c - schema_l) %>% 
        
        ggplot(aes(x='difference',
                   y=schema_c_minus_schema_l)) +
        geom_violin() +
        geom_boxplot(width=0.1,
                     fatten=4,
                     outlier.shape = '') +
        geom_jitter(height = 0,
                    width = 0.06,
                    alpha = 0.3) +
        stat_summary(fun=mean,
                     color='red',
                     size=1) +
        ggtitle('Block 2, Near-PA, schema-c vs schema-l') +
        geom_hline(yintercept = 0, linetype = 'dashed')

```

## Bayes Factor

```{r bf-analysis-near-schema-c-vs-schema-l}

data_for_bf_2 <- data_summary %>%
        filter(type == 'near') %>%
        droplevels() %>%
        
        pivot_wider(id_cols = c(ptp,
                                counterbalancing,
                                type),
                    names_from = condition,
                    values_from = block_2_mouse_error_mean) %>% 
        mutate(schema_c_minus_schema_l = schema_c - schema_l) %>% 
        select(schema_c_minus_schema_l) %>% .[[1]]


null_interval <- c(0,Inf)

bf <- reportBF(ttestBF(
        data_for_bf_2,
        nullInterval = null_interval
)[1],4)

```

